Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Finish section 5

In this section, we present an algorithm for \textsc{Online Multiclass
Classification with Bandit Feedback} and prove an upper bound on the number of
mistakes under the assumption that the examples are strongly linearly separable
with a margin. The algorithm is stated as
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
the mistake upper bound is stated as
\autoref{theorem:strongly-separable-example-mistake-upper-bound}.

@@

\begin{theorem}[Mistake upper bound]
\label{theorem:strongly-separable-example-mistake-upper-bound}
Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
$V \times \{1,2,\dots,K\}$ such that
\begin{enumerate}
  \item the examples are strongly linearly separable with margin $\gamma$ (Definition~\ref{definition:strong-linear-separability}),
  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$,
\end{enumerate}
then the
expected number of mistakes
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
makes is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

@@

The upper bound $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$ on the expected number of
mistakes of
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
optimal to within constant factor as long as the number of classes $K$ is
at most $O((R/\gamma)^2)$. This is proved in
\autoref{theorem:strongly-separable-example-mistake-lower-bound} below.

\begin{theorem}[Mistake lower bound]
\label{theorem:strongly-separable-example-mistake-lower-bound}
Let $\gamma$ be a positive real number, and $R$ be a non-negative real
number. For any (possibly randomized) algorithm $\calA$ for the \textsc{Online
Multiclass Classification with Bandit Feedback} with $K \le
(R/\gamma)^2$ classes there exists an inner product space $(V,
\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
number of mistakes $\calA$ makes is at least $\frac{K-1}{2} \left\lfloor
\frac{1}{4} (R/\gamma)^2 \right\rfloor$.
\end{theorem}

>>>>

In this section, we present an algorithm for \textsc{Online Multiclass
Classification with Bandit Feedback} and prove an upper bound on the number of
mistakes under the assumption that the examples are strongly linearly separable
with a margin. The algorithm is stated as
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} and
the mistake upper bound is stated as
\autoref{theorem:strongly-separable-examples-mistake-upper-bound}.

@@

\begin{theorem}[Mistake upper bound]
\label{theorem:strongly-separable-examples-mistake-upper-bound}
Let $(V, \ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
$V \times \{1,2,\dots,K\}$ such that
\begin{enumerate}
  \item the examples are strongly linearly separable with margin $\gamma$ (Definition~\ref{definition:strong-linear-separability}),
  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$,
\end{enumerate}
then the
expected number of mistakes
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
makes is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

@@

The upper bound $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$ on the expected number of
mistakes of
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
optimal to within constant factor as long as the number of classes $K$ is
at most $O((R/\gamma)^2)$. This is proved in
\autoref{theorem:strongly-separable-examples-mistake-lower-bound} below.

\begin{theorem}[Mistake lower bound]
\label{theorem:strongly-separable-examples-mistake-lower-bound}
Let $\gamma$ be a positive real number, and $R$ be a non-negative real
number. For any (possibly randomized) algorithm $\calA$ for the \textsc{Online
Multiclass Classification with Bandit Feedback} with $K \le
(R/\gamma)^2$ classes there exists an inner product space $(V,
\ip{\cdot}{\cdot})$, a non-negative integer $T$ and a sequence of labeled
examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ in $V \times
\{1,2,\dots,K\}$ that are strongly linearly separable with margin $\gamma$, the
norms satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ and the expected
number of mistakes $\calA$ makes is at least $\frac{K-1}{2} \left\lfloor
\frac{1}{4} (R/\gamma)^2 \right\rfloor$.
\end{theorem}

### 2019-01-14 ICML-submission/from-weak-separability-to-strong-separability.tex
Finish section 5

\section{From linear separability to strong linear separability}
\label{section:from-linear-separability-to-strong-linear-separability}

In this section, we construct and analyze a mapping $\phi$ from the unit ball of
$\R^d$ into a infinite-dimensional inner product space that has the property
that if a set of labeled examples in the unit ball is \emph{weakly} linearly
separable with a margin $\gamma$, applying the mapping $\phi$ makes the examples
\emph{strongly} linearly separable with a margin $\gamma'$ and their norms are
bounded by $2$. The parameter $\gamma'$ is a function of the old margin $\gamma$
and the number of classes $K$, and is specified in the
\autoref{theorem:margin-transformation} below.

The domain of $\phi$ is the unit ball of $\R^d$. The co-domain of $\phi$ is the
classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty ~:~
\sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner product
$\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. We index the coordinates of
$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
integers. The mapping is defined by
\begin{align*}
& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \\
& \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
\end{align*}
where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
is the multinomial coefficient. The corresponding kernel is
$$
k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}} \; .
$$
In passing we note that the formula for $k$ implies the mapping $\phi$ is
well defined. Indeed, since $k(x,x) < +\infty$ for any $x$ in the unit
ball of $\R^d$, it means that $\phi(x)$ indeed lies in $\ell_2$.

Equipped with the mapping $\phi$, we can utilize
Algorithm~\ref{algorithm:kernelized} with kernel function $k(x,x') =
\ip{\phi(x)}{\phi(x')}$ and
\autoref{theorem:strongly-separable-example-mistake-upper-bound} from the
previous section and we obtain an algorithm for weakly linearly separable
examples and an upper bound on its number of mistakes.

The idea behind construction and analysis of the mapping $\phi$ is polynomial
approximation. According to the well known Stone-Weierstrass theorem (see
e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
multivariate polynomials uniformly approximate any continuous function.
Intuitively speaking, we use a multivariate polynomial to approximate, on the
unit ball of $\R^d$, the indicator function corresponding to the intersection of
$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
the polynomial to attain arbitrary value. The polynomial separates examples in
one class from examples in the other classes. To be able to quantify $R'$,
$\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we need
to quantify certain parameters of the approximating polynomial. We construct two
different polynomials with different parameters. The parameters are quantified
in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
stated below.

@@

The proofs of the theorems can be found in
Section~\ref{section:proof-of-polynomial-approximation}. The geometric
interpretation of the two regions described in parts 1 and 2 of the theorems is
explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
proved by~\cite{Klivans-Servedio-2008}. In particular, the bounds in parts
1, 2, 3, 4 of the theorems are independent of the dimension $d$.

@@

\begin{lemma}[Norm bound]
\label{lemma:norm-bound}
Let $p:\R^d \to \R$ be a multivariate polynomial.
There exists $c \in \ell_2$ such that $p(x) = \ip{c}{\psi_n(x)}_{\ell_2}$
and $\norm{c}_{\ell_2} \le 2^{\deg(p)/2} \norm{p}$.
\end{lemma}

@@

Since
\begin{align*}
|c_{\alpha_1, \alpha_2, \dots, \alpha_d}|
& \le 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2} |c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \\
& \le 2^{\deg(p)/2} |c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \; ,
\end{align*}
we have
\begin{align*}
\norm{c}_{\ell_2}
& \le 2^{\deg(p)/2} \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} (c'_{\alpha_1, \alpha_2, \dots, \alpha_d})^2} \\
& = 2^{\deg(p)/2} \norm{p} \; .
\end{align*}
\end{proof}

@@

\begin{theorem}[Margin transformation]
\label{theorem:margin-transformation}
Let $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$
labeled examples that are weakly linearly separable with margin $\gamma > 0$
such that $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$.
Let
\begin{align*}
r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(1/\gamma) \right \rceil \\
\gamma_1 & = \frac{1}{2\sqrt{K} \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \\
\gamma_2 & = ??
\end{align*}
Then, the labeled examples $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
(\phi(x_T), y_T)$ are strongly linearly separable with margin $\gamma' =
\max\{\gamma_1, \gamma_2\}$ and $\norm{\phi(x_1)}_{\ell_2},
\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$.
\end{theorem}

\begin{proof}
First osberve that for any $t=1,2,\dots,T$,
$$
\norm{\phi(x_t)}_{\ell_2} = K_{\phi}(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
$$

@@

Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
$1$.
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
imply that there exists multivariate polynomials $p_i:\R^d \to \R$ and $q_i:\R^d
\to \R$ such that
\begin{align*}
\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{\frac{2}{\gamma}} \right\rceil \; , \\
\deg(q_i) & = (2K-5/2) 2^m \\
& \qquad \cdot \left(2^{2s} r(K-1) (4s+2)^2 \right)^{(s+1/2)r(K-1)} \; .
\end{align*}
Futhermore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$, $q_i(x_t) \ge ???$ and if $y_t \neq i$ then $p_i(x_t) \le -1/2$,
$q_i(x) \le - ???$
and
\begin{align*}
\norm{p_i} & \le \left(188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; , \\
\norm{p_i} & \le ??? .
\end{align*}
By \autoref{lemma:norm-bound} there exists $c_i, c_i' \in \ell_2$ such that
$\ip{c_i}{\phi(x)} = p_i(x)$ and $\ip{c_i'}{\phi(x)} = q_i(x)$ and
\begin{align*}
\norm{c_i}_{\ell_2}
& \le \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \\
\norm{c'_i}_{\ell_2} & \le ??? \\
\end{align*}
Define vectors $u_i, u_i' \in \ell_2$ as
\begin{align*}
u_i & = \frac{c_i}{\sqrt{K} \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; . \\
u_i' & = ???
\end{align*}

Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$ and
$\norm{u_1'}^2 + \norm{u_2'}^2 + \dots + \norm{u_K'}^2 \le 1$.
Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$ and
$\ip{u'_{y_t}}{x_t} \ge \gamma_2$
and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
$\ip{u_j}{x_t} \le - \gamma_1$ and $\ip{u'_j}{x_t} \le - \gamma_2$. In other words,
$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
strongly linearly separable with margin $\gamma_1$ and also strongly separable with
margin $\gamma_2$. Therefore, the examples are strongly separable with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
\end{proof}

>>>>

\section{From weak separability to strong separability}
\label{section:from-weak-separability-to-strong-separability}

In this section, we construct and analyze a mapping $\phi$ from the unit ball of
$\R^d$ into a infinite-dimensional inner product space that has the property
that if a set of labeled examples in the unit ball is \emph{weakly} linearly
separable with a margin $\gamma$ after applying the mapping $\phi$ the examples
become \emph{strongly} linearly separable with a margin $\gamma'$ and their
norms are bounded by $2$. The parameter $\gamma'$ is a function of the old
margin $\gamma$ and the number of classes $K$, and is specified in the
\autoref{theorem:margin-transformation} below.

The domain of $\phi$ is the unit ball of $\R^d$. The co-domain of $\phi$ is the
classical real separable Hilbert space $\ell_2 = \{ x \in \R^\infty ~:~
\sum_{i=1}^\infty x_i^2 < + \infty \}$ equipped with the standard inner product
$\ip{x}{x'}_{\ell_2} = \sum_{i=1}^\infty x_i x'_i$. We index the coordinates of
$\ell_2$ by $d$-tuples $(\alpha_1, \alpha_2, \dots, \alpha_d)$ of non-negative
integers. The mapping is defined by
\begin{align*}
& \left(\phi(x_1, x_2, \dots, x_d)\right)_{(\alpha_1, \alpha_2, \dots, \alpha_d)} = x_1^{\alpha_1} x_2^{\alpha_2} \dots x_d^{\alpha_d} \\
& \qquad \cdot \sqrt{2^{-(\alpha_1 + \alpha_2 + \dots + \alpha_d)} \binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d}}
\end{align*}
where $\binom{\alpha_1 + \alpha_2 + \dots + \alpha_d}{\alpha_1, \alpha_2, \dots, \alpha_d} = \frac{(\alpha_1 + \alpha_2 + \dots + \alpha_d)!}{\alpha_1! \alpha_2! \dots \alpha_d!}$
is the multinomial coefficient. The corresponding kernel is
$$
k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2} = \frac{1}{1 - \frac{1}{2}\ip{x}{x'}_{\R^d}} \; .
$$
We note that the formula for $k$ implies that $k(x,x) < +\infty$ for any $x$ in
the unit ball of $\R^d$ and therefore $\phi(x)$ lies in $\ell_2$. We also note
that kernel function $k(x,x')$ can be evaluated in $O(d)$ time.

We derive a mistake bound for Algorithm~\ref{algorithm:kernelized} with kernel
function $k(x,x') = \ip{\phi(x)}{\phi(x')}_{\ell_2}$ by simply invoking
\autoref{theorem:strongly-separable-examples-mistake-upper-bound} with the
modified margin $\gamma'$ from \autoref{theorem:margin-transformation} below.
The mistake bound is stated as \autoref{corollary:weakly-separable-examples-mistake-upper-bound}.

The idea behind construction and analysis of the mapping $\phi$ is polynomial
approximation. According to the well known Stone-Weierstrass theorem (see
e.g.~\citet[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
multivariate polynomials uniformly approximate any continuous function.
Intuitively speaking, we use a multivariate polynomial to approximate, on the
unit ball of $\R^d$, the indicator function corresponding to the intersection of
$m=K-1$ halfspaces. Within margin $\gamma$ along the decision boundary, we allow
the polynomial to attain arbitrary value. The polynomial separates examples in
one class from examples in the other classes. To be able to quantify $\gamma'$
we need to quantify certain parameters of the approximating polynomial. We
construct two different polynomials with different parameters. The parameters
are quantified in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
stated below.

@@

The proofs of the theorems can be found in
Section~\ref{section:proof-of-polynomial-approximation}. The geometric
interpretation of the two regions described in parts 1 and 2 of the theorems is
explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
proved by~\citet{Klivans-Servedio-2008}. In particular, our bounds in parts 1,
2, 3, 4 of
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
are independent of the dimension $d$.

@@

\begin{lemma}[Norm bound]
\label{lemma:norm-bound}
Let $p:\R^d \to \R$ be a multivariate polynomial.
There exists $c \in \ell_2$ such that $p(x) = \ip{c}{\phi(x)}_{\ell_2}$
and $\norm{c}_{\ell_2} \le 2^{\deg(p)/2} \norm{p}$.
\end{lemma}

@@

Since
\begin{align*}
|c_{\alpha_1, \alpha_2, \dots, \alpha_d}|
& \le 2^{(\alpha_1 + \alpha_2 + \dots + \alpha_d)/2} |c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \\
& \le 2^{\deg(p)/2} |c'_{\alpha_1, \alpha_2, \dots, \alpha_d}| \; ,
\end{align*}
we have
\begin{align*}
\norm{c}_{\ell_2}
& \le 2^{\deg(p)/2} \sqrt{\sum_{\alpha_1, \alpha_2, \dots, \alpha_d} (c'_{\alpha_1, \alpha_2, \dots, \alpha_d})^2} \\
& = 2^{\deg(p)/2} \norm{p} \; . \qquad \qedhere
\end{align*}
\end{proof}

@@

\begin{theorem}[Margin transformation]
\label{theorem:margin-transformation}
Let $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$
labeled examples that are weakly linearly separable with margin $\gamma > 0$
such that $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$.
Let
\begin{align*}
r & = 2 \left\lceil \frac{1}{4} \log_2(4K-3) \right\rceil + 1 \quad \text{and} \quad s = \left \lceil \log_2(2/\gamma) \right \rceil \\
\gamma_1 & = \frac{1}{2\sqrt{K}}  \\
& \ \cdot \left(376 \lceil \log_2(2m) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{-\frac{1}{2} \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; , \\
\gamma_2 & = \frac{2^{s(s+1)r(K-1)} }{4(2K-5/2) 2^{K-1}} \\
& \ \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)} \; .
\end{align*}
Then, the labeled examples $(\phi(x_1), y_1), (\phi(x_2), y_2), \dots,
(\phi(x_T), y_T)$ are strongly linearly separable with margin $\gamma' =
\max\{\gamma_1, \gamma_2\}$ and $\norm{\phi(x_1)}_{\ell_2},
\norm{\phi(x_2)}_{\ell_2}, \dots, \norm{\phi(x_T)}_{\ell_2} \le 2$.
\end{theorem}

\begin{proof}
First osberve that for any $t=1,2,\dots,T$,
$$
\norm{\phi(x_t)}_{\ell_2} = k(x_t,x_t) = \frac{1}{1 - \frac{1}{2} \norm{x_t}^2} \le 2 \; .
$$

@@

Fix any $i \in \{1,2,\dots,K\}$. Consider the $K-1$ vectors $(w_i - w_j)/2$ for
$j \in \{1,2,\dots,K\} \setminus \{i\}$. Note that the vectors have norm at most
$1$.
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
imply that there exists multivariate polynomials $p_i:\R^d \to \R$ and $q_i:\R^d
\to \R$ such that
\begin{align*}
\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{\frac{2}{\gamma}} \right\rceil \; , \\
\deg(q_i) & = (2s+1) r(K-1) \; .
\end{align*}
Futhermore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
$q_i(x_t) \ge \frac{1}{4} \cdot 2^{s(s+1)r(K-1)}$ and if $y_t \neq i$ then
$p_i(x_t) \le -1/2$, $q_i(x) \le - \frac{1}{4} \cdot 2^{s(s+1)r(K-1)}$ and
\begin{align*}
\norm{p_i} & \le \left(188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; , \\
\norm{q_i} & \le (2K-5/2) 2^{K-1} \\
& \qquad \cdot \left(2^{2s} r(K-1) (4s+2)^2 \right)^{(s+1/2)r(K-1)} \; .
\end{align*}
By \autoref{lemma:norm-bound} there exists $c_i, c_i' \in \ell_2$ such that
$\ip{c_i}{\phi(x)} = p_i(x)$ and $\ip{c_i'}{\phi(x)} = q_i(x)$ and
\begin{align*}
\norm{c_i}_{\ell_2}
& \le \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \\
\norm{c'_i}_{\ell_2} & \le (2K-5/2) 2^{K-1} \\
& \qquad \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{(s+1/2)r(K-1)} \; .
\end{align*}
Define vectors $u_i, u_i' \in \ell_2$ as
\begin{align*}
u_i & = \frac{c_i}{\sqrt{K} \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; . \\
u_i' & = \frac{c_i'  \cdot \left(2^{2s+1} r(K-1) (4s+2)^2 \right)^{-(s+1/2)r(K-1)}}{(2K-5/2) 2^{K-1}} \; .
\end{align*}

Then, $\norm{u_1}^2 + \norm{u_2}^2 + \dots + \norm{u_K}^2 \le 1$ and
$\norm{u_1'}^2 + \norm{u_2'}^2 + \dots + \norm{u_K'}^2 \le 1$.
Futhermore, for all $t=1,2,\dots,T$, $\ip{u_{y_t}}{x_t} \ge \gamma_1$ and
$\ip{u'_{y_t}}{x_t} \ge \gamma_2$
and for all $j \in \{1,2,\dots,K\} \setminus \{y_t\}$,
$\ip{u_j}{x_t} \le - \gamma_1$ and $\ip{u'_j}{x_t} \le - \gamma_2$. In other words,
$(\phi(x_1), y_1), (\phi(x_2), y_2), \dots, (\phi(x_T), y_T)$ are
strongly linearly separable with margin $\gamma_1$ and also strongly linearly
separable with margin $\gamma_2$. Therefore, the examples are strongly separable
with margin $\gamma' = \max\{\gamma_1, \gamma_2\}$.
\end{proof}

As a corollary of \autoref{theorem:margin-transformation} and
\autoref{theorem:strongly-separable-examples-mistake-upper-bound}
we get the mistake bound for Algorithm~\ref{algorithm:kernelized}
under the weak separability condition.

\begin{corollary}[Mistake upper bound]
\label{corollary:weakly-separable-examples-mistake-upper-bound}
Let $K$ be a positive
integer, $\gamma$ be a positive real number, $R$ be a non-negative real number. If
$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
$V \times \{1,2,\dots,K\}$ such that
\begin{enumerate}
  \item the examples are weakly linearly separable with margin $\gamma$ (Definition~\ref{definition:weak-linear-separability}),
  \item $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le 1$,
\end{enumerate}
then the expected number of mistakes
Algorithm~\ref{algorithm:kernelized}
makes is at most $2^{\widetilde{O}(\min(K \log^2
\frac{1}{\gamma}, \sqrt{\frac{1}{\gamma}} \log K))}$.
\end{corollary}
